---
title: "Nutrition_Labels_PreProcessing"
author: "Patrick, Josephine & Niels"
date: "2023-12-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
pacman::p_load(
  tidyverse, #for ggplot, dplyr etc
  data.table, #for data.tables 
  plotrix, #for std.error function
  lme4, #for multilevel modelling
  sjPlot, #for table output
  emmeans, #for extracting estimated marginal means for planned contrasts
)
```

```{r}
# SETTING WORKING DIRECTORY - ONLY ONE THAT NEEDS TO BE CHANGE.
## Change it to the location of bachelor_s_coding folder
knitr::opts_knit$set(root.dir = '/Users/niels/Documents/Bachelor_s_coding/')
setwd("/Users/niels/Documents/Bachelor_s_coding/")
```

# splitting the survey into two parts & computing survey variables
```{r}
Sur <- read_csv("final_survey.csv")
# Split the data based on columns
survey_NP <- Sur[, c("ID", paste0("Q", 13:(ncol(Sur)-1)))]

#taking the average of survey questions
survey_NP <- survey_NP %>% 
  rowwise() %>%
  mutate(avg_value = mean(c(Q13, Q14, Q15, Q16, Q17, Q18, Q19)))
```

## Adding variables to the NP data set (left side)
### First adding all the products and calories, and prices for the respective products
```{r}
products <- c("Chips", "Saftevand", "Leverpostej", "Peanuts", "Granola", "Cheddar Cheese", "Yoghurt", "Müsli Bar", "Italiensk Salad", "Gummy Mix", "Regular Milk", "Kakao", "White Bread", "Caramel Ice cream", "Chocolate spread", "Fried Chicken Wings", "Fried Fish Fillets", "Flødeboller", "Regular Pasta", "Pasta sauce", "Ice coffee", "Corn snacks", "Regular Butter", "Dried Banana chips", "Gifler", "Millionbøf", "Lemon soda", "Cheese Dip", "Rosiner", "Mayonaise", "Chips", "Saftevand", "Leverpostej", "Peanuts", "Müsli / Granola", "Cheddar Cheese", "Yoghurt", "Müsli Bar", "Italiensk Salad", "Gummy Mix", "Regular Milk", "Kakao", "White Bread", "Caramel Ice cream", "Chocolate spread", "Fried Chicken Wings", "Fried Fish Fillets", "Flødeboller", "Regular Pasta", "Pasta sauce", "Ice coffee", "Corn snacks", "Regular Butter", "Dried Banana chips", "Gifler", "Millionbøf", "Lemon soda", "Cheese Dip", "Rosiner", "Mayonaise", "Rice Cakes", "Tranebær saft", "Hummus", "Almonds", "Oats", "Cottage Cheese", "Skyr", "Protein müslibar", "Veggiepålæg", "Dried Fruit", "Oat Milk", "Protein Kakao", "Ryebread", "Plain vanilla icecream", "Peanut Butter", "Kyllingestrimler", "Salmon", "Unsweetened Dark Chocolate", "Brown rice", "Hakkede tomater", "Ice coffee sugar free", "Popcorn", "Vegan spread", "Edamame cup", "Carrot cake", "Færdigret", "Sportsdrink", "Salsa", "Saltstænger", "Ketchup")

price <- c(10.5, 7.95, 13.95, 9.25, 32.95, 23.95, 14.95, 10, 12.95, 20, 11.25, 12.95, 14.95, 36.25, 26.95, 30, 27.95, 19.95, 9.95, 12, 12.95, 18.5, 11.7, 12, 16.95, 21.75, 14.5, 10.95, 8.5, 10, 10.5, 7.95, 13.95, 9.25, 32.95, 23.95, 14.95, 10, 12.95, 20, 11.25, 12.95, 14.95, 36.25, 26.95, 30, 27.95, 19.95, 9.95, 12, 12.95, 18.5, 11.7, 12, 16.95, 21.75, 14.5, 10.95, 8.5, 10, 6.5, 19.95, 23.95, 24.75, 9.25, 19.95, 22.95, 9.95, 15.95, 11.95, 14.5, 15.95, 8.95, 36.25, 33.95, 30, 49, 14.95, 12.95, 7.95, 29.95, 6.95, 15.95, 14.95, 28.95, 28, 9, 10.5, 6.5, 14.95)

calories <- c(537, 146, 312, 620, 486, 418, 124, 497, 314, 350, 87, 149, 253, 436, 524, 286, 324, 399, 286, 156, 390, 428, 646, 513, 454, 247, 124, 167, 346, 598, 537, 146, 312, 620, 486, 418, 124, 497, 314, 350, 87, 149, 253, 436, 524, 286, 324, 399, 286, 156, 390, 428, 646, 513, 454, 247, 124, 167, 346, 598, 143, 66, 187, 314, 216, 78, 60, 287, 136, 231, 27, 51, 201, 232, 342, 121, 228, 318, 216, 25, 7, 186, 222, 137, 227, 153, 18, 60, 201, 105)
```

## Adding actual variables for the NP dataset
```{r}
# Loading the NP behavioral data
beh_NP <- read_csv("NP_CSV_Beh.csv")

# adding lookup dataframe containing the actual price, product name, calories, saliency and healthiness of the product
lookup_np_r <- data.frame(
  right_stim = 1:90, 
  Product_R = products,
  Price_R = price,
  Calories_R = calories,
  Healthy_R = c(rep(0, 60), rep(1, 30)),
  Salient_R = c(rep(0, 30), rep(1, 30), rep(0, 30))
)

# Merging the 
df_np <- merge(beh_NP, lookup_np_r, by = "right_stim", all = TRUE)

# Assuming new_df has been initialized with your 1800 rows and the Nr column
# Now, let's add columns to the new_df to store the mapped values
beh_NP$Product_R <- NA
beh_NP$Price_R <- NA
beh_NP$Calories_R <- NA
beh_NP$Healthy_R <- NA
beh_NP$Salient_R <- NA

# Iterate through each row in new_df
for(i in 1:nrow(beh_NP)){
  
  # Find the corresponding row in lookup_df
  corresponding_row <- lookup_np_r[lookup_np_r$right_stim == beh_NP$right_stim[i],]
  
  # Assign values to new_df
  beh_NP$Product_R[i] <- corresponding_row$Product_R
  beh_NP$Price_R[i] <- corresponding_row$Price_R
  beh_NP$Calories_R[i] <- corresponding_row$Calories_R
  beh_NP$Healthy_R[i] <- corresponding_row$Healthy_R
  beh_NP$Salient_R[i] <- corresponding_row$Salient_R
}
```

## Making it for the left stimuli
```{r}
# Creating the lookup dataframe for left stimuli
lookup_np_l <- data.frame(
  left_stim = 1:90, 
  Product_L = products,
  Price_L = price,
  Calories_L = calories,
  Healthy_L = c(rep(0, 60), rep(1, 30)),
  Salient_L = c(rep(0, 30), rep(1, 30), rep(0, 30))
)

# Merging the behavioral data with the left lookup dataframe
df_np <- merge(beh_NP, lookup_np_l, by = "left_stim", all = TRUE)

# Assuming beh_NP has been initialized
# Adding new columns for the left stimuli
beh_NP$Product_L <- NA
beh_NP$Price_L <- NA
beh_NP$Calories_L <- NA
beh_NP$Healthy_L <- NA
beh_NP$Salient_L <- NA

# Iterate through each row in beh_NP
for(i in 1:nrow(beh_NP)){
  
  # Find the corresponding row in lookup_np_l
  corresponding_row <- lookup_np_l[lookup_np_l$left_stim == beh_NP$left_stim[i],]
  
  # Assign values to beh_NP
  beh_NP$Product_L[i] <- corresponding_row$Product_L
  beh_NP$Price_L[i] <- corresponding_row$Price_L
  beh_NP$Calories_L[i] <- corresponding_row$Calories_L
  beh_NP$Healthy_L[i] <- corresponding_row$Healthy_L
  beh_NP$Salient_L[i] <- corresponding_row$Salient_L
}

```

## And for the chosen stimulus
```{r}
# Creating the lookup dataframe for chosen stimuli
lookup_np_c <- data.frame(
  Stimulus = 1:90, 
  Product_C = products,
  Price_C = price,
  Calories_C = calories,
  Healthy_C = c(rep(0, 60), rep(1, 30)),
  Salient_C = c(rep(0, 30), rep(1, 30), rep(0, 30))
)

# Merging the behavioral data with the chosen lookup dataframe
df_np <- merge(beh_NP, lookup_np_c, by = "Stimulus", all = TRUE)

# Assuming beh_NP has been initialized
# Adding new columns for the chosen stimuli
beh_NP$Product_C <- NA
beh_NP$Price_C <- NA
beh_NP$Calories_C <- NA
beh_NP$Healthy_C <- NA
beh_NP$Salient_C <- NA

# Iterate through each row in beh_NP
for(i in 1:nrow(beh_NP)){
  
  # Find the corresponding row in lookup_np_c
  corresponding_row <- lookup_np_c[lookup_np_c$Stimulus == beh_NP$Stimulus[i],]
  
  # Assign values to beh_NP
  beh_NP$Product_C[i] <- corresponding_row$Product_C
  beh_NP$Price_C[i] <- corresponding_row$Price_C
  beh_NP$Calories_C[i] <- corresponding_row$Calories_C
  beh_NP$Healthy_C[i] <- corresponding_row$Healthy_C
  beh_NP$Salient_C[i] <- corresponding_row$Salient_C
}

```

# general changes to the behavioral data
```{r}
# adding trial number in the behavioral data for NP
beh_NP <- beh_NP %>% 
  group_by(ID) %>% 
  mutate(trial = row_number()) %>% 
  ungroup()

# changes the trial so its next to the ID column
beh_NP <- beh_NP %>% 
  select(ID, trial, everything())
```

# Loading the eye-tracking data
```{r}
ED_NP <- read.csv("Data_np_edf_new.csv")
```

# Cleaning eye tracking data
```{r}
#Renaming the variables - NP
names(ED_NP) <- tolower(names(ED_NP))
names(ED_NP)[names(ED_NP) == 'recording_session_label'] <- 'sessionid'
names(ED_NP)[names(ED_NP) == 'trial_index'] <- 'trialnumber'
names(ED_NP)[names(ED_NP) == 'current_fix_duration'] <- 'fix_dur'
names(ED_NP)[names(ED_NP) == 'current_fix_index'] <- 'fix_index'
names(ED_NP)[names(ED_NP) == 'current_fix_pupil'] <- 'pupil'
names(ED_NP)[names(ED_NP) == 'current_fix_start'] <- 'fix_starttime'
names(ED_NP)[names(ED_NP) == 'current_fix_x'] <- 'fix_x'
names(ED_NP)[names(ED_NP) == 'current_fix_y'] <- 'fix_y'
names(ED_NP)[names(ED_NP) == 'trial_start_time'] <- 'trial_starttime'

#Fixation x and y coordinates and pupil size are saved as characters with decimals separated using a comma. Let's fix that!
ED_NP$fix_x <- as.numeric(gsub(",", ".", ED_NP$fix_x))
ED_NP$fix_y <- as.numeric(gsub(",", ".", ED_NP$fix_y))
ED_NP$pupil <- as.numeric(gsub(",", ".", ED_NP$pupil))
```


## General changes to the EDF files
```{r}
## MERGING THE EYE-TRACKING DATA AND BEHAVIORAL DATA FOR NP
merged_data_NP <- ED_NP %>%
  left_join(beh_NP, by = c("sessionid" = "ID", "trialnumber" = "trial"))

# ADDING THE SURVEY INFO ALSO
merged_data_NP <- merged_data_NP %>% 
  left_join(survey_NP, by = c("sessionid" = "ID"))

# REMOVING THE QUESTIONS FROM THE MERGED DATA SET
merged_data_NP <- merged_data_NP %>% 
  select(-c(Q13, Q14, Q15, Q16, Q17, Q18, Q19))
```

```{r}
#Checking the plots of where people have looked at the screen
plot(ED_NP$fix_x,ED_NP$fix_y)
```

# Defining the two AOIs
```{r}
# Defining the two AOIs
merged_data_NP$AOI <- case_when(
  merged_data_NP$fix_x > 523 & merged_data_NP$fix_x < 703 & merged_data_NP$fix_y > 657 & merged_data_NP$fix_y < 767 ~ 1,
  merged_data_NP$fix_x > 1361 & merged_data_NP$fix_x < 1543 & merged_data_NP$fix_y > 657 & merged_data_NP$fix_y < 767 ~ 2,
)

#remove data points outside of the four squares / AOIs
merged_data_NP$AOI[is.na(merged_data_NP$AOI)] <- 0
merged_data_NP <- subset(merged_data_NP, AOI != 0) 

plot(merged_data_NP$fix_x,merged_data_NP$fix_y) #how does it look now?
```

# Computing the dwell time for each trial for each of the two AOIs, and the total dwell time per trial - FOR NP DF
```{r}
# computing the dwell time
dwell_NP <- merged_data_NP %>%
  group_by(sessionid, trialnumber) %>%
  summarise(
    AOI1_dwell_time = sum(ifelse(AOI == 1, fix_dur, 0), na.rm = TRUE),
    AOI2_dwell_time = sum(ifelse(AOI == 2, fix_dur, 0), na.rm = TRUE),
    total_dwell_time = sum(fix_dur, na.rm = TRUE)
  ) %>%
  ungroup() %>% 
  rename(ID = sessionid, trial = trialnumber)

# combining the dwell-time df with the behavioral df, so we only have one row per trial.
beh_NP1 <- beh_NP %>% 
  left_join(dwell_NP, by = c("ID", "trial"))


# For the NP dataset, a lot of the trials do not have any fixations on the AOIs. Therefore, it results in NAs when the dwell data set is merged with the behavioral one. Here we replace the NAs with 0s:
beh_NP1[, c("AOI1_dwell_time", "AOI2_dwell_time", "total_dwell_time")] <- lapply(beh_NP1[, c("AOI1_dwell_time", "AOI2_dwell_time", "total_dwell_time")], function(x) ifelse(is.na(x), 0, x))

write.csv(beh_NP1, "Jose_Final_Data.csv")
```