---
title: "Sustainability_Labels_PreProcessing"
author: "Patrick, Josephine & Niels"
date: "2023-12-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
pacman::p_load(
  tidyverse, #for ggplot, dplyr etc
  data.table, #for data.tables 
  plotrix, #for std.error function
  lme4, #for multilevel modelling
  sjPlot, #for table output
  emmeans, #for extracting estimated marginal means for planned contrasts
)
```

```{r}
# SETTING WORKING DIRECTORY - ONLY ONE THAT NEEDS TO BE CHANGE.
## Change it to the location of bachelor_s_coding folder
knitr::opts_knit$set(root.dir = '/Users/niels/Documents/Bachelor_s_coding/')
setwd("/Users/niels/Documents/Bachelor_s_coding/")
```

# splitting the survey into two parts & computing survey variables
```{r}
Sur <- read_csv("final_survey.csv")
# Split the data based on columns
survey_J <- Sur[, c("ID", paste0("Q", 1:12))]

#taking the average of survey questions
survey_J <- survey_J %>% 
  rowwise() %>%
  mutate(avg_value = mean(c(Q1, Q2, Q3, Q4, Q5, Q6, Q7, Q8, Q9)))

```

## Adding variables to the Jose data set (left side)
```{r}
#Loading the behavioral data
beh_J <- read.csv("Jose_CSV_Beh_new.csv")

#Adjustments of general DataFrame - Left product
lookup_df <- data.frame(
  left_stim = c(1:30),
  Product_L = c(rep("Pork", 10), rep("Chicken", 10), rep("Fish", 10)),
  Label_L = c(rep("A", 4), rep("C", 2), rep("E", 4), 
            rep("A", 4), rep("C", 2), rep("E", 4), 
            rep("A", 4), rep("C", 2), rep("E", 4)),
  Salience_L = c("High", "High", "Low", "Low", 
               "High", "Low", 
               "High", "High", "Low", "Low",
               "High", "High", "Low", "Low", 
               "High", "Low", 
               "High", "High", "Low", "Low",
               "High", "High", "Low", "Low", 
               "High", "Low", 
               "High", "High", "Low", "Low"),
  Price_L = c(45, 50, 45, 50, 
            40, 40, 
            35, 30, 35, 30, 
            45, 50, 45, 50, 
            40, 40, 
            35, 30, 35, 30, 
            45, 50, 45, 50, 
            40, 40, 
            35, 30, 35, 30),
  Price_level_L = c("low", "high", "low", "high", 
                  "40", "40", 
                  "low", "high", "low", "high",
                  "low", "high", "low", "high", 
                  "40", "40", 
                  "low", "high", "low", "high",
                  "low", "high", "low", "high", 
                  "40", "40", 
                  "low", "high", "low", "high")
)

# Now, merging this lookup_df with new_df
new_df <- merge(beh_J, lookup_df, by = "left_stim", all = TRUE)

# Assuming new_df has been initialized with your 1800 rows and the Nr column
# Now, let's add columns to the new_df to store the mapped values
beh_J$Product_L <- NA
beh_J$Label_L <- NA
beh_J$Salience_L <- NA
beh_J$Price_L <- NA
beh_J$Price_level_L <- NA

# Iterate through each row in new_df
for(i in 1:nrow(beh_J)){
  
  # Find the corresponding row in lookup_df
  corresponding_row <- lookup_df[lookup_df$left_stim == beh_J$left_stim[i],]
  
  # Assign values to new_df
  beh_J$Product_L[i] <- corresponding_row$Product_L
  beh_J$Label_L[i] <- corresponding_row$Label_L
  beh_J$Salience_L[i] <- corresponding_row$Salience_L
  beh_J$Price_L[i] <- corresponding_row$Price_L
  beh_J$Price_level_L[i] <- corresponding_row$Price_level_L
}
```

## Adding variables to the Jose data set (right side)
```{r}
#Adjustments of general DataFrame - Right product
lookup_df <- data.frame(
  right_stim = c(1:30),
  Product_R = c(rep("Pork", 10), rep("Chicken", 10), rep("Fish", 10)),
  Label_R = c(rep("A", 4), rep("C", 2), rep("E", 4), 
            rep("A", 4), rep("C", 2), rep("E", 4), 
            rep("A", 4), rep("C", 2), rep("E", 4)),
  Salience_R = c("High", "High", "Low", "Low", 
               "High", "Low", 
               "High", "High", "Low", "Low",
               "High", "High", "Low", "Low", 
               "High", "Low", 
               "High", "High", "Low", "Low",
               "High", "High", "Low", "Low", 
               "High", "Low", 
               "High", "High", "Low", "Low"),
  Price_R = c(45, 50, 45, 50, 
            40, 40, 
            35, 30, 35, 30, 
            45, 50, 45, 50, 
            40, 40, 
            35, 30, 35, 30, 
            45, 50, 45, 50, 
            40, 40, 
            35, 30, 35, 30),
  Price_level_R = c("low", "high", "low", "high", 
                  "40", "40", 
                  "low", "high", "low", "high",
                  "low", "high", "low", "high", 
                  "40", "40", 
                  "low", "high", "low", "high",
                  "low", "high", "low", "high", 
                  "40", "40", 
                  "low", "high", "low", "high")
)

# Now, merging this lookup_df with new_df
new_df <- merge(beh_J, lookup_df, by = "right_stim", all = TRUE)

# Assuming new_df has been initialized with your 1800 rows and the Nr column
# Now, let's add columns to the new_df to store the mapped values
beh_J$Product_R <- NA
beh_J$Label_R <- NA
beh_J$Salience_R <- NA
beh_J$Price_R <- NA
beh_J$Price_level_R <- NA

# Iterate through each row in new_df
for(i in 1:nrow(beh_J)){
  
  # Find the corresponding row in lookup_df
  corresponding_row <- lookup_df[lookup_df$right_stim == beh_J$right_stim[i],]
  
  # Assign values to new_df
  beh_J$Product_R[i] <- corresponding_row$Product_R
  beh_J$Label_R[i] <- corresponding_row$Label_R
  beh_J$Salience_R[i] <- corresponding_row$Salience_R
  beh_J$Price_R[i] <- corresponding_row$Price_R
  beh_J$Price_level_R[i] <- corresponding_row$Price_level_R
}
```

## Adding variables to the Jose data set (chosen product)
```{r}
#Adjustments of general DataFrame - Chosen product

# Creating a fixed lookup dataframe
lookup_df <- data.frame(
  Stimulus = c(1:30),
  Product_C = c(rep("Pork", 10), rep("Chicken", 10), rep("Fish", 10)),
  Label_C = c(rep("A", 4), rep("C", 2), rep("E", 4), 
            rep("A", 4), rep("C", 2), rep("E", 4), 
            rep("A", 4), rep("C", 2), rep("E", 4)),
  Salience_C = c("High", "High", "Low", "Low", 
               "High", "Low", 
               "High", "High", "Low", "Low",
               "High", "High", "Low", "Low", 
               "High", "Low", 
               "High", "High", "Low", "Low",
               "High", "High", "Low", "Low", 
               "High", "Low", 
               "High", "High", "Low", "Low"),
  Price_C = c(45, 50, 45, 50, 
            40, 40, 
            35, 30, 35, 30, 
            45, 50, 45, 50, 
            40, 40, 
            35, 30, 35, 30, 
            45, 50, 45, 50, 
            40, 40, 
            35, 30, 35, 30),
  Price_level_C = c("low", "high", "low", "high", 
                  "40", "40", 
                  "low", "high", "low", "high",
                  "low", "high", "low", "high", 
                  "40", "40", 
                  "low", "high", "low", "high",
                  "low", "high", "low", "high", 
                  "40", "40", 
                  "low", "high", "low", "high")
)

# Now, merging this lookup_df with new_df
new_df <- merge(beh_J, lookup_df, by = "Stimulus", all = TRUE)

# Assuming new_df has been initialized with your 1800 rows and the Nr column
# Now, let's add columns to the new_df to store the mapped values
beh_J$Product_C <- NA
beh_J$Label_C <- NA
beh_J$Salience_C <- NA
beh_J$Price_C <- NA
beh_J$Price_level_C <- NA

# Iterate through each row in new_df
for(i in 1:nrow(beh_J)){
  
  # Find the corresponding row in lookup_df
  corresponding_row <- lookup_df[lookup_df$Stimulus == beh_J$Stimulus[i],]
  
  # Assign values to new_df
  beh_J$Product_C[i] <- corresponding_row$Product_C
  beh_J$Label_C[i] <- corresponding_row$Label_C
  beh_J$Salience_C[i] <- corresponding_row$Salience_C
  beh_J$Price_C[i] <- corresponding_row$Price_C
  beh_J$Price_level_C[i] <- corresponding_row$Price_level_C
}
```

# general changes to the behavioral data
```{r}
# adding trial number in the behavioral data for Jose
beh_J <- beh_J %>% 
  group_by(ID) %>% 
  mutate(trial = row_number()) %>% 
  ungroup()

# changes the trial so its next to the ID column
beh_J <- beh_J %>% 
  select(ID, trial, everything())

beh_J <- beh_J %>% 
  left_join(survey_J, by = "ID") %>% 
  select(-c(Q1, Q2, Q3, Q4, Q5, Q6, Q7, Q8, Q9, Q10, Q11, Q12))
```

# Loading the eye-tracking data
```{r}
ED_J <-  read.csv("Data_Jose_ED_new.csv")
```

# Cleaning eye tracking data
```{r}
#Renaming the variables - J
names(ED_J) <- tolower(names(ED_J))
names(ED_J)[names(ED_J) == 'recording_session_label'] <- 'sessionid'
names(ED_J)[names(ED_J) == 'trial_index'] <- 'trialnumber'
names(ED_J)[names(ED_J) == 'current_fix_duration'] <- 'fix_dur'
names(ED_J)[names(ED_J) == 'current_fix_index'] <- 'fix_index'
names(ED_J)[names(ED_J) == 'current_fix_pupil'] <- 'pupil'
names(ED_J)[names(ED_J) == 'current_fix_start'] <- 'fix_starttime'
names(ED_J)[names(ED_J) == 'current_fix_x'] <- 'fix_x'
names(ED_J)[names(ED_J) == 'current_fix_y'] <- 'fix_y'
names(ED_J)[names(ED_J) == 'trial_start_time'] <- 'trial_starttime'


#Fixation x and y coordinates and pupil size are saved as characters with decimals separated using a comma. Let's fix that!
ED_J$fix_x <- as.numeric(gsub(",", ".", ED_J$fix_x))
ED_J$fix_y <- as.numeric(gsub(",", ".", ED_J$fix_y))
ED_J$pupil <- as.numeric(gsub(",", ".", ED_J$pupil))
```

## General changes to the EDF files
```{r}
#filtering out the trials containing products that the participant indicated they did not like (< 3 in survey score).

#pork
exclude_pork_ids <- survey_J %>%
  filter(Q10 < 3) %>%
  pull(ID)

#chicken
exclude_chicken_ids <- survey_J %>%
  filter(Q11 < 3) %>%
  pull(ID)

#fish
exclude_fish_ids <- survey_J %>%
  filter(Q12 < 3) %>%
  pull(ID)

# Excluding trials for participants who rated Pork under 3
beh_J <- beh_J %>%
  filter(!(ID %in% exclude_pork_ids & (Product_L == "Pork" | Product_R == "Pork")))

# Excluding trials for participants who rated Chicken under 3
beh_J <- beh_J %>%
  filter(!(ID %in% exclude_chicken_ids & (Product_L == "Chicken" | Product_R == "Chicken")))

# Excluding trials for participants who rated Fish under 3
beh_J <- beh_J %>%
  filter(!(ID %in% exclude_fish_ids & (Product_L == "Fish" | Product_R == "Fish")))
```

# Plotting all trials (aggregated) for each participant
```{r}
# Grouping by sessionid (participant) and trialnumber.
df_grouped <- ED_J %>%
  group_by(sessionid, trialnumber) %>%
  summarise(mean_fix_x = mean(fix_x, na.rm = TRUE), 
            mean_fix_y = mean(fix_y, na.rm = TRUE))

# Aggregating all trials for each participant, and plotting them
ggplot(df_grouped, aes(x = mean_fix_x, y = mean_fix_y)) +
  geom_point() + 
  facet_wrap(~sessionid, nrow = 5) +  # Display 5 participants per row
  labs(title = "Aggregated Fixation Points for Each Trial of Every Participant",
       x = "Mean X Coordinate",
       y = "Mean Y Coordinate") +
  theme_minimal()
```

```{r}
#Checking the plots of where people have looked at the screen
plot(ED_J$fix_x,ED_J$fix_y)
```

# Defining the two AOIs on the screen
```{r}
# Defining the two AOIs
ED_J$AOI <- case_when(
  ED_J$fix_x > 215 & ED_J$fix_x < 267 & ED_J$fix_y > 509 & ED_J$fix_y < 582 ~ 1,
  ED_J$fix_x > 1058 & ED_J$fix_x < 1107 & ED_J$fix_y > 509 & ED_J$fix_y < 582 ~ 2,
)

#remove data points outside of the four squares / AOIs
ED_J$AOI[is.na(ED_J$AOI)] <- 0
ED_J <- subset(ED_J, AOI != 0) 

plot(ED_J$fix_x,ED_J$fix_y) #how does it look now?
```

# Computing the dwell time for each trial for each of the two AOIs, and the total dwell time per trial
```{r}
# computing the dwell time
dwell_J <- ED_J %>%
  group_by(sessionid, trialnumber) %>%
  summarise(
    AOI1_dwell_time = sum(ifelse(AOI == 1, fix_dur, 0), na.rm = TRUE),
    AOI2_dwell_time = sum(ifelse(AOI == 2, fix_dur, 0), na.rm = TRUE),
    total_dwell_time = sum(fix_dur, na.rm = TRUE)
  ) %>%
  ungroup() %>% 
  rename(ID = sessionid, trial = trialnumber)

# combining the dwell-time df with the behavioral df, so we only have one row per trial.
beh_J1 <- beh_J %>% 
  left_join(dwell_J, by = c("ID", "trial"))

# For the J dataset, a lot of the trials do not have any fixations on the AOIs. Therefore, it results in NAs when the dwell data set is merged with the behavioral one. Here we replace the NAs with 0s:
beh_J1[, c("AOI1_dwell_time", "AOI2_dwell_time", "total_dwell_time")] <- lapply(beh_J1[, c("AOI1_dwell_time", "AOI2_dwell_time", "total_dwell_time")], function(x) ifelse(is.na(x), 0, x))

write.csv(beh_J1, "Jose_Final_Data.csv")
```